This markdown plots the following:
UMAPs of different integrations.
violin plots of the entropies and local struct (figure 3).

Load packages.
```{r message=FALSE}
library(Seurat)
library(ggplot2)
library(ggpubr)
```

Load the batch effect data frames.
```{r}
setwd("./BEffects")
HW_BE_I <- readRDS("HW_BE_I.RDS")
HW_BE_II <- readRDS("HW_BE_II.RDS")
HW_BE_III <- readRDS("HW_BE_III.RDS")
HW_BE_IV <- readRDS("HW_BE_IV.RDS")
HW_BE_V <- readRDS("HW_BE_V.RDS")
HW_BE_VI <- readRDS("HW_BE_VI.RDS")
```

Generate the input lists for the norm plots and the integrated batch effects.
```{r}
norm_list <- list()
norm_list[["I"]] <- HW_BE_I
norm_list[["II"]] <- HW_BE_II
norm_list[["III"]] <- HW_BE_III
norm_list[["IV"]] <- HW_BE_IV
norm_list[["V"]] <- HW_BE_V
norm_list[["VI"]] <- HW_BE_VI

int_list <- list()
int_list[["I"]] <- HW_BE_I
int_list[["II"]] <- HW_BE_II
int_list[["III"]] <- HW_BE_III
int_list[["IV"]] <- HW_BE_IV
int_list[["VI"]] <- HW_BE_VI
```

Clear memory.
```{r}
rm(list = setdiff(ls(), c("norm_list", "int_list")))
```

First Write a fuction for int_list.
RNA, SCT 
cca, rpca, harmony
entropy, localstruct

from all data frames and plots the violin diagrams with the specific colorcode.
```{r}
Int_plot <- function(layer, reduc, metric) {
#layer <- "RNA"
#reduc <- "harmony"
#metric <- "entropy"

call <- paste(layer, reduc, sep = "_")
metadata <- c("pool", "sample", "celltype")
setup <- c("I", "II", "III", "IV", "VI")
ggplotlist <- list()

for (j in metadata) {
  n <- 1
  for (i in setup) {
    df_temp <- int_list[[i]][[j]][[call]][[metric]]
    df_temp$setup <- rep(i, dim(df_temp)[1])
    
    if (n == 1) {
      collect <- df_temp
    }
    if (n > 1) {
      collect <- rbind(collect, df_temp)
    }
    n <- n + 1
  }
  collect$setup <- factor(collect$setup, levels = setup)
  ggplotlist[[j]] <- collect
}

#I <- "#D81B60"
#II <- "#987201"
#III <- "#078872"
#IV <- "#751C1C"
#V <- "#F4A9C7"
#V <- "#1E88E5"

# plot
plot_list <- list()
for (n in 1:3) {
  colour <- c("#D81B60", "#987201", "#078872", "#751C1C", "#1E88E5")
  if ((n == 2) & (metric == "entropy")) {
    colour <- c("#D81B60", "#078872", "#751C1C", "#1E88E5")
  } 
  #colnames(ggplotlist[[metadata[n]]])
  #if (metric == "entropy") {
  plot_list[[n]] <- ggplot(ggplotlist[[metadata[n]]], 
                         aes(setup, .data[[colnames(ggplotlist[[metadata[n]]])[1]]], fill = setup)) + 
  geom_violin() +
  scale_fill_manual(values = colour) +
  geom_boxplot(width=0.1, fill="white", outlier.size = 0.3) +
  stat_summary(fun=mean, geom="point", shape=20, size=3, color="black", fill="black") +
  theme_bw() + NoLegend() +
  theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.text = element_blank()) +
  theme(axis.title = element_blank()) + ylim(c(0, 1)) #+
  #theme(plot.margin = margin(t = .1, r = .1, b = .6, l = .1, unit = "cm"))
  #}
  
}

plot <- ggarrange(plotlist = plot_list, nrow = 1, ncol = 3)

return(plot)
}
```

Plot the unintegrated data - Norm_list.
```{r}
#metadata <- c("pool", "sample", "hash", "hashwell", "celltype")
metadata <- c("pool", "sample", "celltype")
setup <- c("I", "II", "III", "IV", "V", "VI")

ggplotnorm <- list()

for (j in metadata) {
  n <- 1
  for (i in setup) {
    if (i == "V") {
      df_temp <- norm_list[[i]][[j]]
    }
    if (i != "V") {
      df_temp <- norm_list[[i]][[j]]$RNA_unint
    }
    df_temp$setup <- rep(i, dim(df_temp)[1])
    
    if (n == 1) {
      collect <- df_temp
    }
    if (n > 1) {
      collect <- rbind(collect, df_temp)
    }
    n <- n + 1
  }
  collect$setup <- factor(collect$setup, levels = setup)
  ggplotnorm[[j]] <- collect
}

plot_list <- list()
for (n in 1:3) {
  colour <- c("#D81B60", "#987201", "#078872", "#751C1C", "#F4A9C7",  "#1E88E5")
  if ((n == 2)) {
    colour <- c("#D81B60", "#078872", "#751C1C", "#F4A9C7", "#1E88E5")
  } 
  if ((n == 1)) {
    colour <- c("#D81B60", "#987201", "#078872", "#751C1C",  "#1E88E5")
  } 

  plot_list[[n]] <- ggplot(ggplotnorm[[metadata[n]]], 
                         aes(setup, .data[[colnames(ggplotnorm[[metadata[n]]])[1]]], fill = setup)) + 
  geom_violin() +
  scale_fill_manual(values = colour) +
  geom_boxplot(width=0.1, fill="white", outlier.size = 0.3) +
  stat_summary(fun=mean, geom="point", shape=20, size=3, color="black", fill="black") +
  theme_bw() + NoLegend() +
  theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.text = element_blank()) +
  theme(axis.title = element_blank()) + ylim(c(0, 1)) +
  theme(plot.margin = margin(t = .1, r = .1, b = .6, l = .1, unit = "cm"))
}

plot <- ggarrange(plotlist = plot_list, nrow = 3, ncol = 1)
```

Create the individual plots serially.
```{r}
RNA_harmony_entropy <- Int_plot(layer <- "RNA", reduc <- "harmony", metric <- "entropy")
RNA_cca_entropy <- Int_plot(layer <- "RNA", reduc <- "cca", metric <- "entropy")
RNA_rpca_entropy <- Int_plot(layer <- "RNA", reduc <- "rpca", metric <- "entropy")


SCT_harmony_entropy <- Int_plot(layer <- "SCT", reduc <- "harmony", metric <- "entropy")
SCT_cca_entropy <- Int_plot(layer <- "SCT", reduc <- "cca", metric <- "entropy")
SCT_rpca_entropy <- Int_plot(layer <- "SCT", reduc <- "rpca", metric <- "entropy")
```

Know the medians of sample entropy and pool entropy in V and II respectively.
```{r}
pool_thresh <- median(norm_list$II$pool$RNA_unint$entropy)

sample_thresh <- median(norm_list$V$sample$entropy)
```

Calculate % of cells above a given entropy threshold.
```{r}
pct_calc <- function(array, thresh) {
#array <- norm_list$I$pool$RNA_unint$entropy
#array <- int_list$I$pool$RNA_cca$entropy$entropy
pct_out <- (length(which(array > thresh))/length(array))*100

return(pct_out)
}
```
Calc pct.
```{r}
pct_calc(norm_list$I$pool$RNA_unint$entropy, pool_thresh)
pct_calc(norm_list$II$pool$RNA_unint$entropy, pool_thresh)
pct_calc(norm_list$III$pool$RNA_unint$entropy, pool_thresh)
pct_calc(norm_list$IV$pool$RNA_unint$entropy, pool_thresh)
pct_calc(norm_list$VI$pool$RNA_unint$entropy, pool_thresh)

pct_calc(norm_list$I$sample$RNA_unint$entropy, sample_thresh)
pct_calc(norm_list$III$sample$RNA_unint$entropy, sample_thresh)
pct_calc(norm_list$IV$sample$RNA_unint$entropy, sample_thresh)
pct_calc(norm_list$V$sample$entropy, sample_thresh)
pct_calc(norm_list$VI$sample$RNA_unint$entropy, sample_thresh)

pct_calc(int_list$I$pool$RNA_rpca$entropy$entropy, pool_thresh)
pct_calc(int_list$II$pool$RNA_rpca$entropy$entropy, pool_thresh)
pct_calc(int_list$III$pool$RNA_rpca$entropy$entropy, pool_thresh)
pct_calc(int_list$IV$pool$RNA_rpca$entropy$entropy, pool_thresh)
pct_calc(int_list$VI$pool$RNA_rpca$entropy$entropy, pool_thresh)

pct_calc(int_list$I$pool$SCT_rpca$entropy$entropy, pool_thresh)
#pct_calc(int_list$II$pool$SCT_rpca$entropy$entropy, pool_thresh)
pct_calc(int_list$III$pool$SCT_rpca$entropy$entropy, pool_thresh)
pct_calc(int_list$IV$pool$SCT_rpca$entropy$entropy, pool_thresh)
pct_calc(int_list$VI$pool$SCT_rpca$entropy$entropy, pool_thresh)

pct_calc(int_list$I$sample$SCT_rpca$entropy$entropy, sample_thresh)
pct_calc(int_list$III$sample$SCT_rpca$entropy$entropy, sample_thresh)
pct_calc(int_list$IV$sample$SCT_rpca$entropy$entropy, sample_thresh)
pct_calc(int_list$VI$sample$SCT_rpca$entropy$entropy, sample_thresh)
```
Bar diagram of pool.
```{r}
bar_pool <- c()
bar_pool <- c(bar_pool, pct_calc(norm_list$I$pool$RNA_unint$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(norm_list$III$pool$RNA_unint$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(norm_list$IV$pool$RNA_unint$entropy, pool_thresh))
bar_pool <- c(bar_pool, pct_calc(norm_list$VI$pool$RNA_unint$entropy, pool_thresh))
bar_pool <- c(bar_pool,0)
bar_pool <- c(bar_pool,pct_calc(int_list$I$pool$RNA_harmony$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$III$pool$RNA_harmony$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$IV$pool$RNA_harmony$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$V$pool$RNA_harmony$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,0)
bar_pool <- c(bar_pool,pct_calc(int_list$I$pool$RNA_cca$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$III$pool$RNA_cca$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$IV$pool$RNA_cca$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$V$pool$RNA_cca$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,0)
bar_pool <- c(bar_pool,pct_calc(int_list$I$pool$RNA_rpca$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$III$pool$RNA_rpca$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$IV$pool$RNA_rpca$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$V$pool$RNA_rpca$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,0)
bar_pool <- c(bar_pool,pct_calc(int_list$I$pool$SCT_harmony$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$III$pool$SCT_harmony$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$IV$pool$SCT_harmony$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$V$pool$SCT_harmony$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,0)
bar_pool <- c(bar_pool,pct_calc(int_list$I$pool$SCT_cca$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$III$pool$SCT_cca$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$IV$pool$SCT_cca$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$V$pool$SCT_cca$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,0)
bar_pool <- c(bar_pool,pct_calc(int_list$I$pool$SCT_rpca$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$III$pool$SCT_rpca$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$IV$pool$SCT_rpca$entropy$entropy, pool_thresh))
bar_pool <- c(bar_pool,pct_calc(int_list$V$pool$SCT_rpca$entropy$entropy, pool_thresh))

bar_pool_data <- data.frame(serial <- 1:34, bar_pool)
colnames(bar_pool_data) <- c("serial", "bar_pool")

col <- c("#D81B60", "#078872", "#751C1C", "#1E88E5", "#FFFFFF")
setup <- c("I", "III", "IV", "VI", "null",
           "I", "III", "IV", "VI", "null",
           "I", "III", "IV", "VI", "null",
           "I", "III", "IV", "VI", "null",
           "I", "III", "IV", "VI", "null",
           "I", "III", "IV", "VI", "null",
           "I", "III", "IV", "VI")
bar_pool_data$setup <- factor(setup, levels = c("I", "III", "IV", "VI", "null"))
ggplot(bar_pool_data, aes(serial, bar_pool, fill = setup)) + geom_bar(stat="identity") +
  scale_fill_manual(values = col) + theme_bw() + NoLegend() +
  theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.text = element_blank()) +
  theme(axis.title = element_blank()) + scale_y_continuous(breaks = c(25,50))
```
Bar diagram of sample.
```{r}
bar_sample <- c()
bar_sample <- c(bar_sample, pct_calc(norm_list$I$sample$RNA_unint$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(norm_list$III$sample$RNA_unint$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(norm_list$IV$sample$RNA_unint$entropy, sample_thresh))
bar_sample <- c(bar_sample, pct_calc(norm_list$VI$sample$RNA_unint$entropy, sample_thresh))
bar_sample <- c(bar_sample,0)
bar_sample <- c(bar_sample,pct_calc(int_list$I$sample$RNA_harmony$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$III$sample$RNA_harmony$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$IV$sample$RNA_harmony$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$V$sample$RNA_harmony$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,0)
bar_sample <- c(bar_sample,pct_calc(int_list$I$sample$RNA_cca$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$III$sample$RNA_cca$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$IV$sample$RNA_cca$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$V$sample$RNA_cca$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,0)
bar_sample <- c(bar_sample,pct_calc(int_list$I$sample$RNA_rpca$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$III$sample$RNA_rpca$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$IV$sample$RNA_rpca$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$V$sample$RNA_rpca$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,0)
bar_sample <- c(bar_sample,pct_calc(int_list$I$sample$SCT_harmony$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$III$sample$SCT_harmony$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$IV$sample$SCT_harmony$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$V$sample$SCT_harmony$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,0)
bar_sample <- c(bar_sample,pct_calc(int_list$I$sample$SCT_cca$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$III$sample$SCT_cca$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$IV$sample$SCT_cca$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$V$sample$SCT_cca$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,0)
bar_sample <- c(bar_sample,pct_calc(int_list$I$sample$SCT_rpca$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$III$sample$SCT_rpca$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$IV$sample$SCT_rpca$entropy$entropy, sample_thresh))
bar_sample <- c(bar_sample,pct_calc(int_list$V$sample$SCT_rpca$entropy$entropy, sample_thresh))

bar_sample_data <- data.frame(serial <- 1:34, bar_sample)
colnames(bar_sample_data) <- c("serial", "bar_sample")

col <- c("#D81B60", "#078872", "#751C1C", "#1E88E5", "#FFFFFF")
setup <- c("I", "III", "IV", "VI", "null",
           "I", "III", "IV", "VI", "null",
           "I", "III", "IV", "VI", "null",
           "I", "III", "IV", "VI", "null",
           "I", "III", "IV", "VI", "null",
           "I", "III", "IV", "VI", "null",
           "I", "III", "IV", "VI")
bar_sample_data$setup <- factor(setup, levels = c("I", "III", "IV", "VI", "null"))
ggplot(bar_sample_data, aes(serial, bar_sample, fill = setup)) + geom_bar(stat="identity") +
  scale_fill_manual(values = col) + theme_bw() + NoLegend() +
  theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.text = element_blank()) +
  theme(axis.title = element_blank()) + scale_y_continuous(breaks = c(25,50))
```


Load the Seurat objects.
Note: These data is not part of the current repository because of their size.
These are Seurat objects generated and saved by the script hash_well_01.Rmd using the .h5 files in ./data.
```{r message=FALSE}
setwd("./SObjects") # set directory where the integrated objects are saved
hash_well_I_RNA <- readRDS("hash_well_I_RNA.RDS")
hash_well_I_SCT <- readRDS("hash_well_I_SCT.RDS")
hash_well_II_RNA <- readRDS("hash_well_II_RNA.RDS")
hash_well_II_SCT <- readRDS("hash_well_II_SCT.RDS")
hash_well_III_RNA <- readRDS("hash_well_III_RNA.RDS")
hash_well_III_SCT <- readRDS("hash_well_III_SCT.RDS")
hash_well_IV_RNA <- readRDS("hash_well_IV_RNA.RDS")
hash_well_IV_SCT <- readRDS("hash_well_IV_SCT.RDS")
hash_well_V_RNA <- readRDS("hash_well_V_RNA.RDS")
hash_well_VI_RNA <- readRDS("hash_well_VI_RNA.RDS")
hash_well_VI_SCT <- readRDS("hash_well_VI_SCT.RDS")
```


```{r}
convert_sample <- function(object) {
#object <- hash_well_V_RNA
sample <- c()
for (i in object$HTO_maxID) {
  if (i %in% c("Ms.Hashtag-1","Ms.Hashtag-2")) {
    sample <- c(sample, "Aalpha")
    next
  }
  if (i %in% c("Ms.Hashtag-3","Ms.Hashtag-4")) {
    sample <- c(sample, "Bbeta")
    next
  }
  if (i %in% c("Ms.Hashtag-5","Ms.Hashtag-6")) {
    sample <- c(sample, "cgamma")
    next
  }
  if (i %in% c("Ms.Hashtag-7","Ms.Hashtag-8")) {
    sample <- c(sample, "Ddelta")
    next
  }
  if (i %in% c("Ms.Hashtag-9","Ms.Hashtag-12")) {
    sample <- c(sample, "Eepsilon")
    next
  }
  if (i %in% c("Ms.Hashtag-13","Ms.Hashtag-14")) {
    sample <- c(sample, "Fzeta")
    next
  }
}

object$sample <- sample
}
```

Write a function to make the dimplots: pools.
```{r}
DimPlot_pools <- function(object, reduc, ptsize) {
#object <- hash_well_I_RNA
col <- c('#C77CFF','#00C19A','#CD9600','#F8766D','#B19470','#00B8E7')

level <- unique(object$orig.ident)
level <- level[order(level)]

object$orig.ident.factor <- factor(object$orig.ident, levels = level)

P <- DimPlot(object, reduction = reduc, raster=TRUE, pt.size = ptsize,
        group.by = "orig.ident.factor", label = FALSE, cols = col[1:length(level)]) + NoLegend()

return(P)
}
```

Write a function to make the dimplots: samples.
```{r}
DimPlot_samples <- function(object, reduc, ptsize) {
#object <- hash_well_I_RNA
object$sample <- convert_sample(object)
col <- c('#C77CFF','#00C19A','#CD9600','#F8766D','#B19470','#00B8E7')
samples <- c("Aalpha", "Bbeta", "cgamma","Ddelta","Eepsilon","Fzeta")
level <- unique(object$sample)
level <- level[order(level)]

object$sample.factor <- factor(object$sample, levels = level)

P <- DimPlot(object, reduction = reduc, raster=TRUE, pt.size = ptsize,
        group.by = "sample.factor", label = FALSE, 
        cols = col[samples %in% level]) + NoLegend()

return(P)
}
```

Call the dimplot_pools function serially and generate the plot.
```{r}
p <- vector(mode = "list", length = 30)
#hash_well_I_RNA 
p[[1]] <- DimPlot_pools(hash_well_I_RNA, reduc = "umap.harmony", ptsize = 1.5) 
p[[2]] <- DimPlot_pools(hash_well_I_RNA, reduc = "umap.cca", ptsize = 1.5) 
p[[3]] <- DimPlot_pools(hash_well_I_RNA, reduc = "umap.rpca", ptsize = 1.5)
#hash_well_I_SCT 
p[[4]] <- DimPlot_pools(hash_well_I_SCT, reduc = "umap.harmony", ptsize = 1.5)
p[[5]] <- DimPlot_pools(hash_well_I_SCT, reduc = "umap.cca", ptsize = 1.5)
p[[6]] <- DimPlot_pools(hash_well_I_SCT, reduc = "umap.rpca", ptsize = 1.5)
#hash_well_II_RNA 
p[[7]] <- DimPlot_pools(hash_well_II_RNA, reduc = "umap.harmony", ptsize = 2)
p[[8]] <- DimPlot_pools(hash_well_II_RNA, reduc = "umap.cca", ptsize = 2)
p[[9]] <- DimPlot_pools(hash_well_II_RNA, reduc = "umap.rpca", ptsize = 2)
#hash_well_II_SCT 
p[[10]] <- DimPlot_pools(hash_well_II_SCT, reduc = "umap.harmony", ptsize = 2) 
p[[11]] <- DimPlot_pools(hash_well_II_SCT, reduc = "umap.cca", ptsize = 2)
p[[12]] <- DimPlot_pools(hash_well_II_SCT, reduc = "umap.rpca", ptsize = 2) 
#hash_well_III_RNA 
p[[13]] <- DimPlot_pools(hash_well_III_RNA, reduc = "umap.harmony", ptsize = 1.5) 
p[[14]] <- DimPlot_pools(hash_well_III_RNA, reduc = "umap.cca", ptsize = 1.5) 
p[[15]] <- DimPlot_pools(hash_well_III_RNA, reduc = "umap.rpca", ptsize = 1.5) 
#hash_well_III_SCT 
p[[16]] <- DimPlot_pools(hash_well_III_SCT, reduc = "umap.harmony", ptsize = 1.5)
p[[17]] <- DimPlot_pools(hash_well_III_SCT, reduc = "umap.cca", ptsize = 1.5) 
p[[18]] <- DimPlot_pools(hash_well_III_SCT, reduc = "umap.rpca", ptsize = 1.5) 
#hash_well_IV_RNA 
p[[19]] <- DimPlot_pools(hash_well_IV_RNA, reduc = "umap.harmony", ptsize = 1.5) 
p[[20]] <- DimPlot_pools(hash_well_IV_RNA, reduc = "umap.cca", ptsize = 1.5) 
p[[21]] <- DimPlot_pools(hash_well_IV_RNA, reduc = "umap.rpca", ptsize = 1.5) 
#hash_well_IV_SCT 
p[[22]] <- DimPlot_pools(hash_well_IV_SCT, reduc = "umap.harmony", ptsize = 1.5) 
p[[23]] <- DimPlot_pools(hash_well_IV_SCT, reduc = "umap.cca", ptsize = 1.5) 
p[[24]] <- DimPlot_pools(hash_well_IV_SCT, reduc = "umap.rpca", ptsize = 1.5)
#hash_well_VI_RNA 
p[[25]] <- DimPlot_pools(hash_well_VI_RNA, reduc = "umap.harmony", ptsize = 1.5) 
p[[26]] <- DimPlot_pools(hash_well_VI_RNA, reduc = "umap.cca", ptsize = 1.5) 
p[[27]] <- DimPlot_pools(hash_well_VI_RNA, reduc = "umap.rpca", ptsize = 1.5) 
#hash_well_VI_SCT 
p[[28]] <- DimPlot_pools(hash_well_VI_SCT, reduc = "umap.harmony", ptsize = 1.5) 
p[[29]] <- DimPlot_pools(hash_well_VI_SCT, reduc = "umap.cca", ptsize = 1.5) 
p[[30]] <- DimPlot_pools(hash_well_VI_SCT, reduc = "umap.rpca", ptsize = 1.5)
```

Generate the UMAP figures.
```{r}
for(i in 1:length(p)) {
  p[[i]] <- p[[i]] + NoAxes() + labs(title = as.character(i)) +
  theme(plot.margin = unit(c(-0.8,-0.5,-0.6,-0.5), "lines"), plot.title = element_text(size=0)) + #
  theme(plot.title = element_text(size=0))
  #theme(plot.margin = unit(c(0.1,-0.2,-0.3,-0.2), "lines")) +
  #theme(plot.title = element_text(size=20)) 
  #+ labs(title = def_CITE[i]) 
  #+ ggtitle("")
}

fig1 <- ggarrange(plotlist = p[1:18],ncol=3,nrow=6)
fig2 <- ggarrange(plotlist = p[19:30],ncol=3,nrow=6)
#plot(fig1)
```

Call the dimplot_samples function serially and generate the plot.
```{r}
p <- vector(mode = "list", length = 30)
#hash_well_I_RNA 
p[[1]] <- DimPlot_samples(hash_well_I_RNA, reduc = "umap.harmony", ptsize = 1.5) 
p[[2]] <- DimPlot_samples(hash_well_I_RNA, reduc = "umap.cca", ptsize = 1.5) 
p[[3]] <- DimPlot_samples(hash_well_I_RNA, reduc = "umap.rpca", ptsize = 1.5)
#hash_well_I_SCT 
p[[4]] <- DimPlot_samples(hash_well_I_SCT, reduc = "umap.harmony", ptsize = 1.5)
p[[5]] <- DimPlot_samples(hash_well_I_SCT, reduc = "umap.cca", ptsize = 1.5)
p[[6]] <- DimPlot_samples(hash_well_I_SCT, reduc = "umap.rpca", ptsize = 1.5)
#hash_well_II_RNA 
p[[7]] <- DimPlot_samples(hash_well_II_RNA, reduc = "umap.harmony", ptsize = 2)
p[[8]] <- DimPlot_samples(hash_well_II_RNA, reduc = "umap.cca", ptsize = 2)
p[[9]] <- DimPlot_samples(hash_well_II_RNA, reduc = "umap.rpca", ptsize = 2)
#hash_well_II_SCT 
p[[10]] <- DimPlot_samples(hash_well_II_SCT, reduc = "umap.harmony", ptsize = 2) 
p[[11]] <- DimPlot_samples(hash_well_II_SCT, reduc = "umap.cca", ptsize = 2)
p[[12]] <- DimPlot_samples(hash_well_II_SCT, reduc = "umap.rpca", ptsize = 2) 
#hash_well_III_RNA 
p[[13]] <- DimPlot_samples(hash_well_III_RNA, reduc = "umap.harmony", ptsize = 1.5) 
p[[14]] <- DimPlot_samples(hash_well_III_RNA, reduc = "umap.cca", ptsize = 1.5) 
p[[15]] <- DimPlot_samples(hash_well_III_RNA, reduc = "umap.rpca", ptsize = 1.5) 
#hash_well_III_SCT 
p[[16]] <- DimPlot_samples(hash_well_III_SCT, reduc = "umap.harmony", ptsize = 1.5)
p[[17]] <- DimPlot_samples(hash_well_III_SCT, reduc = "umap.cca", ptsize = 1.5) 
p[[18]] <- DimPlot_samples(hash_well_III_SCT, reduc = "umap.rpca", ptsize = 1.5) 
#hash_well_IV_RNA 
p[[19]] <- DimPlot_samples(hash_well_IV_RNA, reduc = "umap.harmony", ptsize = 1.5) 
p[[20]] <- DimPlot_samples(hash_well_IV_RNA, reduc = "umap.cca", ptsize = 1.5) 
p[[21]] <- DimPlot_samples(hash_well_IV_RNA, reduc = "umap.rpca", ptsize = 1.5) 
#hash_well_IV_SCT 
p[[22]] <- DimPlot_samples(hash_well_IV_SCT, reduc = "umap.harmony", ptsize = 1.5) 
p[[23]] <- DimPlot_samples(hash_well_IV_SCT, reduc = "umap.cca", ptsize = 1.5) 
p[[24]] <- DimPlot_samples(hash_well_IV_SCT, reduc = "umap.rpca", ptsize = 1.5)
#hash_well_VI_RNA 
p[[25]] <- DimPlot_samples(hash_well_VI_RNA, reduc = "umap.harmony", ptsize = 1.5) 
p[[26]] <- DimPlot_samples(hash_well_VI_RNA, reduc = "umap.cca", ptsize = 1.5) 
p[[27]] <- DimPlot_samples(hash_well_VI_RNA, reduc = "umap.rpca", ptsize = 1.5) 
#hash_well_VI_SCT 
p[[28]] <- DimPlot_samples(hash_well_VI_SCT, reduc = "umap.harmony", ptsize = 1.5) 
p[[29]] <- DimPlot_samples(hash_well_VI_SCT, reduc = "umap.cca", ptsize = 1.5) 
p[[30]] <- DimPlot_samples(hash_well_VI_SCT, reduc = "umap.rpca", ptsize = 1.5)
```

Generate the UMAP figures.
```{r}
for(i in 1:length(p)) {
  p[[i]] <- p[[i]] + NoAxes() + labs(title = as.character(i)) +
  theme(plot.margin = unit(c(-0.8,-0.5,-0.6,-0.5), "lines"), plot.title = element_text(size=0)) + #
  theme(plot.title = element_text(size=0))
  #theme(plot.margin = unit(c(0.1,-0.2,-0.3,-0.2), "lines")) +
  #theme(plot.title = element_text(size=20)) 
  #+ labs(title = def_CITE[i]) 
  #+ ggtitle("")
}

fig1 <- ggarrange(plotlist = p[1:18],ncol=3,nrow=6)
fig2 <- ggarrange(plotlist = p[19:30],ncol=3,nrow=6)
#plot(fig1)
```

UMAP for setup V.
```{r}
plot1 <- DimPlot_samples(hash_well_V_RNA, reduc = "umap.unint", ptsize = 2) 
```

The UMAP with color legends for main text: revision 2 (response to reviewer 3).
```{r}
DimPlot(hash_well_I_SCT, reduction = "umap.rpca", group.by = "rpca_clusters")
```

Analysis of abundance across conditions (response to reviewer 3).
Extract abundance of cells in each cluster in each condition/sample in each pipeline outcome.

Function to include the sample metadata in the Seurat objects.
```{r}
sample_metadata <- function(object) {

sample <- c()
for (i in object$HTO_maxID) {
  if (i %in% c("Ms.Hashtag-1","Ms.Hashtag-2")) {
    sample <- c(sample, "alpha")
    next
  }
  if (i %in% c("Ms.Hashtag-3","Ms.Hashtag-4")) {
    sample <- c(sample, "beta")
    next
  }
  if (i %in% c("Ms.Hashtag-5","Ms.Hashtag-6")) {
    sample <- c(sample, "gamma")
    next
  }
  if (i %in% c("Ms.Hashtag-7","Ms.Hashtag-8")) {
    sample <- c(sample, "delta")
    next
  }
  if (i %in% c("Ms.Hashtag-9","Ms.Hashtag-12")) {
    sample <- c(sample, "epsilon")
    next
  }
  if (i %in% c("Ms.Hashtag-13","Ms.Hashtag-14")) {
    sample <- c(sample, "zeta")
    next
  }
}

object$sample <- sample
return(object)
}
```

Function for extraction of cluster sizes.
```{r}
clustsize_probe <- function(object) {
# object <- hash_well_I_RNA
#object <- sample_metadata(object)
# split the object on conditions and clusters
clust_size <- c(length(levels(object$harmony_clusters)),
length(levels(object$cca_clusters)),
length(levels(object$rpca_clusters)))

return(clust_size)
}
```

Function for extraction of cluster vs sample tables.
```{r}
clustsample_probe <- function(object) {
# object <- hash_well_I_RNA
object <- sample_metadata(object)
# split the object on conditions and clusters
harmony_table <- table(object$harmony_clusters, object$sample)
cca_table <- table(object$cca_clusters, object$sample)
rpca_table <- table(object$rpca_clusters, object$sample)

clust_tables <- list(harmony_table, cca_table, rpca_table)
return(clust_tables)
}
```

Cluster size table.
```{r}
hash_well_I_RNA_clust <- clustsize_probe(hash_well_I_RNA)
hash_well_I_SCT_clust <- clustsize_probe(hash_well_I_SCT)

hash_well_II_RNA_clust <- clustsize_probe(hash_well_II_RNA)
hash_well_II_SCT_clust <- clustsize_probe(hash_well_II_SCT)

hash_well_III_RNA_clust <- clustsize_probe(hash_well_III_RNA)
hash_well_III_SCT_clust <- clustsize_probe(hash_well_III_SCT)

hash_well_IV_RNA_clust <- clustsize_probe(hash_well_IV_RNA)
hash_well_IV_SCT_clust <- clustsize_probe(hash_well_IV_SCT)

hash_well_VI_RNA_clust <- clustsize_probe(hash_well_VI_RNA)
hash_well_VI_SCT_clust <- clustsize_probe(hash_well_VI_SCT)

clust_size_table <- data.frame(c(hash_well_I_RNA_clust, hash_well_I_SCT_clust),
                               c(hash_well_II_RNA_clust, hash_well_II_SCT_clust),
                               c(hash_well_III_RNA_clust, hash_well_III_SCT_clust),
                               c(hash_well_IV_RNA_clust, hash_well_IV_SCT_clust),
                               c(hash_well_VI_RNA_clust, hash_well_VI_SCT_clust))

colnames(clust_size_table) <- c("I", "II", "III", "IV", "VI")
```

Sample, celltype level stats.
```{r}
hash_well_I_RNA_clustsample <- clustsample_probe(hash_well_I_RNA)
hash_well_I_SCT_clustsample <- clustsample_probe(hash_well_I_SCT)

hash_well_II_RNA_clustsample <- clustsample_probe(hash_well_II_RNA)
hash_well_II_SCT_clustsample <- clustsample_probe(hash_well_II_SCT)

hash_well_III_RNA_clustsample <- clustsample_probe(hash_well_III_RNA)
hash_well_III_SCT_clustsample <- clustsample_probe(hash_well_III_SCT)

hash_well_IV_RNA_clustsample <- clustsample_probe(hash_well_IV_RNA)
hash_well_IV_SCT_clustsample <- clustsample_probe(hash_well_IV_SCT)

hash_well_VI_RNA_clustsample <- clustsample_probe(hash_well_VI_RNA)
hash_well_VI_SCT_clustsample <- clustsample_probe(hash_well_VI_SCT)
```

A function to calculate coefficient of variation for each row.
Get the average CV and CI of CV for each sample clust table.
```{r}
cv_calc <- function(object) {
#object <- hash_well_I_RNA_clustsample

object_h <- as.data.frame.matrix(object[[1]])
object_c <- as.data.frame.matrix(object[[2]])
object_r <- as.data.frame.matrix(object[[3]])

cv_h <- c()
cv_c <- c()
cv_r <- c()

for (k in 1:dim(object_h)[1]) {
  cv_h <- c(cv_h, (sd(as.numeric(object_h[k,]), na.rm = TRUE) / mean(as.numeric(object_h[k,]), na.rm = TRUE)) * 100)
}

for (k in 1:dim(object_c)[1]) {
  cv_c <- c(cv_c, (sd(as.numeric(object_c[k,]), na.rm = TRUE) / mean(as.numeric(object_c[k,]), na.rm = TRUE)) * 100)
}

for (k in 1:dim(object_r)[1]) {
  cv_r <- c(cv_r, (sd(as.numeric(object_r[k,]), na.rm = TRUE) / mean(as.numeric(object_r[k,]), na.rm = TRUE)) * 100)
}

cv_h_mean <- round(mean(cv_h), digits = 2)
cv_c_mean <- round(mean(cv_c), digits = 2)
cv_r_mean <- round(mean(cv_r), digits = 2)

cv_h_se <- round(1.96*(sd(cv_h)/sqrt(length(cv_h))), digits = 2)
cv_c_se <- round(1.96*(sd(cv_c)/sqrt(length(cv_c))), digits = 2)
cv_r_se <- round(1.96*(sd(cv_r)/sqrt(length(cv_r))), digits = 2)

return(c(cv_h_mean, cv_c_mean, cv_r_mean, cv_h_se, cv_c_se, cv_r_se))
}
```

Now generate the table of averaged CV and error margins.
```{r}
hash_well_I_RNA_cv <- cv_calc(hash_well_I_RNA_clustsample) 
hash_well_I_SCT_cv <- cv_calc(hash_well_I_SCT_clustsample) 

hash_well_III_RNA_cv <- cv_calc(hash_well_III_RNA_clustsample) 
hash_well_III_SCT_cv <- cv_calc(hash_well_III_SCT_clustsample) 

hash_well_IV_RNA_cv <- cv_calc(hash_well_IV_RNA_clustsample) 
hash_well_IV_SCT_cv <- cv_calc(hash_well_IV_SCT_clustsample) 

hash_well_VI_RNA_cv <- cv_calc(hash_well_VI_RNA_clustsample) 
hash_well_VI_SCT_cv <- cv_calc(hash_well_VI_SCT_clustsample) 

cv_mean_table <- data.frame(c(hash_well_I_RNA_cv[1:3], hash_well_I_SCT_cv[1:3]),
                               c(hash_well_III_RNA_cv[1:3], hash_well_III_SCT_cv[1:3]),
                               c(hash_well_IV_RNA_cv[1:3], hash_well_IV_SCT_cv[1:3]),
                               c(hash_well_VI_RNA_cv[1:3], hash_well_VI_SCT_cv[1:3]))
colnames(cv_mean_table) <- c("I", "III", "IV", "VI")

cv_se_table <- data.frame(c(hash_well_I_RNA_cv[4:6], hash_well_I_SCT_cv[4:6]),
                               c(hash_well_III_RNA_cv[4:6], hash_well_III_SCT_cv[4:6]),
                               c(hash_well_IV_RNA_cv[4:6], hash_well_IV_SCT_cv[4:6]),
                               c(hash_well_VI_RNA_cv[4:6], hash_well_VI_SCT_cv[4:6]))
colnames(cv_se_table) <- c("I", "III", "IV", "VI")
```

Function to carry out Kruskal Wallis test on the columns to show that variation does not change across conditions.
```{r}
KruskalT <- function(object, removealpha) {
#object <- hash_well_VI_RNA_clustsample

object_h <- as.list(as.data.frame.matrix(object[[1]]))
object_c <- as.list(as.data.frame.matrix(object[[2]]))
object_r <- as.list(as.data.frame.matrix(object[[3]]))

if (removealpha == "yes") {
  object_h$alpha <- NULL
  object_c$alpha <- NULL
  object_r$alpha <- NULL
}
h_pval <- kruskal.test(object_h)
c_pval <- kruskal.test(object_c)
r_pval <- kruskal.test(object_r)

h_pval <- round(h_pval$p.value, digits = 2)
c_pval <- round(c_pval$p.value, digits = 2)
r_pval <- round(r_pval$p.value, digits = 2)

return(c(h_pval, c_pval, r_pval))
}
```

Now generate the table of averaged CV and error margins.
```{r}
hash_well_I_RNA_kpval <- KruskalT(hash_well_I_RNA_clustsample, "no") 
hash_well_I_SCT_kpval <- KruskalT(hash_well_I_SCT_clustsample, "no") 

hash_well_III_RNA_kpval <- KruskalT(hash_well_III_RNA_clustsample, "no") 
hash_well_III_SCT_kpval <- KruskalT(hash_well_III_SCT_clustsample, "no") 

hash_well_IV_RNA_kpval <- KruskalT(hash_well_IV_RNA_clustsample, "no") 
hash_well_IV_SCT_kpval <- KruskalT(hash_well_IV_SCT_clustsample, "no") 

hash_well_VI_RNA_kpval <- KruskalT(hash_well_VI_RNA_clustsample, "yes") 
hash_well_VI_SCT_kpval <- KruskalT(hash_well_VI_SCT_clustsample, "yes") 

kpval_mean_table <- data.frame(c(hash_well_I_RNA_kpval, hash_well_I_SCT_kpval),
                               c(hash_well_III_RNA_kpval, hash_well_III_SCT_kpval),
                               c(hash_well_IV_RNA_kpval, hash_well_IV_SCT_kpval),
                               c(hash_well_VI_RNA_kpval, hash_well_VI_SCT_kpval))
colnames(kpval_mean_table) <- c("I", "III", "IV", "VI")
```




