This markdown integrates the different sets within the hash_well dataset.
The description of the sets are in the figure 1A of the manuscript.
All data are read from and saved at a different directory to keep the repository light.

Load packages.
```{r message=FALSE}
library(Seurat)
library(hdf5r)
library(openxlsx)
library(stringr)

library(future)
options(future.globals.maxSize = 50*1e9)

options(Seurat.object.assay.version = 'v5')
```

Function to remove TCR and BCR genes.
```{r}
filterTCRBCR <- function(rnacounts) {
#rnacounts <- rna.counts

Ighv <- grep('Ighv',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Ighd <- grep('Ighd',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Ighj <- grep('Ighj',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Igkv <- grep('Igkv',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Igkj <- grep('Igkj',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Iglv <- grep('Iglv',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Iglj <- grep('Iglj',rnacounts@Dimnames[[1]], ignore.case = FALSE)

# Collect the indexes to remove Tra, Trb, Trg and Trd genes
Trav <- grep('Trav',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Traj <- grep('Traj',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Trbv <- grep('Trbv',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Trbd <- grep('Trbd',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Trbj <- grep('Trbj',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Trgv <- grep('Trgv',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Trgj <- grep('Trgj',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Trdv <- grep('Trdv',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Trdd <- grep('Trdd',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Trdj <- grep('Trdj',rnacounts@Dimnames[[1]], ignore.case = FALSE)

# Collect the indexes to remove constant region genes
Igha <- grep('Igha',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Ighe <- grep('Ighe',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Ighd <- grep('Ighd',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Ighg <- grep('Ighg',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Ighm <- grep('Ighm',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Ighm <- Ighm[1]
Igkc <- grep('Igkc',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Iglc <- grep('Iglc',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Trac <- grep('Trac',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Trbc <- grep('Trbc',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Tcrg <- grep('Tcrg',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Trdc <- grep('Trdc',rnacounts@Dimnames[[1]], ignore.case = FALSE)
# Collect the indexes to remove mitochondrial genes
mt <- grep('mt-',rnacounts@Dimnames[[1]], ignore.case = FALSE)
# Collect the indexes to remove ribosomal genes
Rpl <- grep('Rpl',rnacounts@Dimnames[[1]], ignore.case = FALSE)
Rps <- grep('Rps',rnacounts@Dimnames[[1]], ignore.case = FALSE)

# Remove Igh, Igk, Igl and Tra, Trb, Trg, Trd from RNA
rnacounts <- rnacounts[-c(Ighv, Ighd, Ighj, Igkv, Igkj, Iglv, Iglj,
                                  Trav, Traj, Trbv, Trbd, Trbj, Trgv, Trgj, 
                                  Trdv, Trdd, Trdj,
                                  Igha, Ighe, Ighd, Ighg, Ighm, 
                                  Igkc, Iglc, Trac, Trbc, Tcrg, 
                                  Trdc, mt, Rpl, Rps),]

return(rnacounts)
}
```

Read files, demultiplex and generate lists.
Then integrate the datasets and save it. After saving clear memory.

hash_well_I <- all six wells 
```{r message=FALSE}
setwd("../hash_well_data")
labl_hsh <- read.xlsx('HW_des.xlsx')
ind_adt <- read.xlsx('adt_ind.xlsx', colNames = FALSE)


setwd('./h5')
for (j in 1:6) {
  D.data <- Read10X_h5(paste('./', labl_hsh$Label[j], '.h5', sep = ""))
  k1 <- str_split(labl_hsh$hashtags_pick[j], " ") # pick up the hashes
  k2 <- as.numeric(k1[[1]])
  k3 <- str_split(ind_adt[1,1], ", ") # pick up the ADT indexes
  k4 <- as.numeric(k3[[1]])
 
  rna.counts <- D.data$`Gene Expression` # Call the data
  hto.counts <- D.data$`Antibody Capture`[k2 + 192, ]
  adt.counts <- D.data$`Antibody Capture`[k4, ]
 
  D.data.joint <- intersect(colnames(rna.counts), colnames(hto.counts)) # Make sure overlapping counts
  D.data.joint <- intersect(colnames(rna.counts), colnames(adt.counts))
  rna.counts <- rna.counts[, D.data.joint]
  hto.counts <- hto.counts[, D.data.joint]
  adt.counts <- adt.counts[, D.data.joint]
  
  # Single line removal of TCR BCR genes
  rna.counts <- filterTCRBCR(rna.counts)
  
  # Create Seurat object
  D <- CreateSeuratObject(counts = rna.counts, project = labl_hsh$Label[j], assay = "RNA") # Seurat object
  D[["percent.mt"]] <- PercentageFeatureSet(D, pattern = "^mt-")
 
  D[["HTO"]] <- CreateAssayObject(counts = hto.counts)
  D <- NormalizeData(D, assay = "HTO", normalization.method = "CLR", verbose = FALSE) # Normalise the HTO
  D[["ADT"]] <- CreateAssayObject(counts = adt.counts)
  D <- NormalizeData(D, assay = "ADT", normalization.method = "CLR", verbose = TRUE) # NOrmalise ADT
  
  # Rename cells to avoid future conflicts
  D$dataset <- labl_hsh$Label[j]
  D <- RenameCells(object = D, add.cell.id = labl_hsh$Label[j])

  # Cleanup
  D <- subset(D, subset = nFeature_RNA > 500 & nFeature_RNA < 3000 & percent.mt < 2.5 & nCount_RNA < 20000)

 # Demultiplexing
  D <- HTODemux(D, assay = "HTO", positive.quantile = 0.99, verbose = TRUE) # Demultiplex
  Idents(D) <- "HTO_classification.global"
  D.singlet <- subset(D, idents = "Singlet")
  
  #SCtransform
  #D.singlet <- SCTransform(D.singlet, vst.flavor = "v2", verbose = FALSE)

  # Annotate samples following the hashtags
  D.singlet@meta.data$orig.id = ""
  for(k in unique(D.singlet@meta.data$HTO_maxID)){
  if (nchar(k) == 12) {
    D.singlet@meta.data$orig.id[D.singlet@meta.data$HTO_maxID == k] = as.character(
                                                  paste(strsplit(labl_hsh[j,1], split = "_")[[1]][2], 
                                                  'H0',gsub("Ms.Hashtag-", "", k), sep = ""))
  }
  if (nchar(k) == 13) {
    D.singlet@meta.data$orig.id[D.singlet@meta.data$HTO_maxID == k] = as.character(
                                                  paste(strsplit(labl_hsh[j,1], split = "_")[[1]][2], 
                                                  'H', gsub("Ms.Hashtag-", "", k), sep = ""))
  }
}

  if (j == 1) {
    mObject <- D.singlet
  }
  if (j > 1)
    mObject <- merge(mObject, D.singlet)
}

DefaultAssay(mObject) <- "RNA"
mObject <- JoinLayers(mObject)
mObject[["RNA"]] <- split(mObject[["RNA"]], f = mObject$dataset)

mObject <- SCTransform(mObject, verbose = FALSE, vst.flavor = 'v2')  # per-layer SCT v2
mObject[["SCT"]] <- split(mObject[["SCT"]], f = mObject$dataset)

#DefaultAssay(mObject) <- "SCT"
mObject <- RunPCA(mObject, npcs = 30, verbose = FALSE)  # PCA on SCT residuals
#iObject <- IntegrateLayers(
#  object = mObject, method = RPCAIntegration,
#  orig.reduction = "pca", new.reduction = "integrated.rpca",
#  assay = "SCT", verbose = FALSE
#)

mObject <- IntegrateLayers(object = mObject, method = HarmonyIntegration,
                       orig.reduction = "pca", new.reduction = 'harmony',
                       assay = "SCT", verbose = FALSE)

mObject <- IntegrateLayers(object = mObject, method = RPCAIntegration,
                       orig.reduction = "pca", new.reduction = 'integrated.rpca',
                       assay = "SCT", verbose = FALSE)
```

hash_well_II <- only control cells from six wells
```{r}

```

hash_well_III <- all six wells without controls
```{r}

```

hash_well_IV <- five wells; pulled well absent
```{r}

```

hash_well_V <- only pulled well
```{r}

```

hash_well_VI <- pulled hashes eliminated
```{r}

```







